Glasgow Hackerspace CIC Articles of Association

### 2024-03-02 articles.tex
Change link colour and set metadata

% Custom section numbering
%'
%' This bit was really annoying, basically we treat sections as top-level
%' titles like in the Book document class. We don't want to number them.
%' Just hiding the section numbering with titlesec means that there's an
%' extra padded section number in front of a given subsection.
%' There are other simpler tricks to do this but these then have the
%' problem of no continuation across sections, i.e. the subsections start
%' numbered from 1 again in each new section!
%'
%' Partly via: https://tex.stackexchange.com/questions/80113/hide-section-numbers-but-keep-numbering/80114#80114
\makeatletter
\renewcommand\thesection{\@arabic\c@section}
\renewcommand\thesubsection{\@arabic\c@subsection}
\renewcommand\thesubsubsection{\@arabic\c@subsection.\@arabic\c@subsubsection}
\makeatother

@@

\begin{document}
\renewcommand\contentsname{
    \centering\bfseries\Large{Index to the Articles}\newline\justifying
}

@@

\subsubsection[Directors' remote decision-making]{A decision which is made in accordance with \fancyref{subsubsubsection:unanimous} shall be as valid and effectual as if it had been passed at a meeting duly convened and held, provided the following conditions are complied with:}\label{subsubsubsection:remotedecision}
\begin{subindentpara}
  \item approval from each Director must be received by one person being either such person as all the Directors have nominated in advance for that purpose or such other person as volunteers if necessary (``the Recipient''), which person may, for the avoidance of doubt, be one of the Directors;
  \item following receipt of responses from all of the Directors, the Recipient must communicate to all of the Directors by any means whether the resolution has been formally approved by the Directors in accordance with this \fancyref{subsubsubsection:remotedecision};
  \item the date of the decision shall be the date of the communication from the Recipient confirming formal approval;
  \item the Recipient must prepare a minute of the decision in accordance with the \fancyref{subsection:minutes}.
\end{subindentpara}
\subsection{Conflicts of interest}
\subsubsection[Directors must declare Conflict of Interests]{Whenever a Director finds themselves in a situation that is reasonably likely to give rise to a Conflict of Interest, they must declare their interest to the Directors unless, or except to the extent that, the other Directors are or ought reasonably to be aware of it already.}
\subsubsection[Directors may debate a potential Conflict of Interest]{If any question arises as to whether a Director has a Conflict of Interest, the question shall be decided by a majority decision of the other Directors.}
\subsubsection[Directors' participation in meetings and Conflict of Interest]{Whenever a matter is to be discussed at a meeting or decided in accordance with \fancyref{subsubsection:withoutmeeting} and a Director has a Conflict of Interest in respect of that matter then, subject to \fancyref{subsubsection:authconflict}, they must:}\label{subsubsubsection:directornovote}
\begin{subindentpara}
  \item remain only for such part of the meeting as in the view of the other Directors is necessary to inform the debate;
  \item not be counted in the quorum for that part of the meeting; and
  \item withdraw during the vote and have no vote on the matter.
\end{subindentpara}
\subsubsection[Disclosure of confidential information relating to Director's Conflict of Interest]{When a Director has a Conflict of Interest which they have declared to the Directors, they shall not be in breach of their duties to the Company by withholding confidential information from the Company if to disclose it would result in a breach of any other duty or obligation of confidence owed by them.}
\subsubsection[Directors' voting at meetings and conflict of interest]{A Director must not vote at a board meeting (or at a meeting of a sub-committee) on any resolution which relates to a matter in which they have a personal interest or duty which conflicts (or may conflict) with the interests of the Hackerspace; they must withdraw from the meeting while an item of that nature is being dealt with.}\label{subsubsubsection:withdraw}
\subsubsection[Definition of a personal interest]{For the purposes of \fancyref{subsubsubsection:withdraw}: a Director will be deemed to have a personal interest in relation to a particular matter if a body in relation to which they are an Employee, Director, Officer or Elected Representative has an interest in the matter.}
\subsubsection[Quorum at Directors' meetings resulting from Conflict of Interest]{If, as a result of a Conflict of Interest (and the Directors have not authorised this Conflict ofIinterest) quorum at a Directors' meeting cannot be reached, the Directors must defer the decision to the membership by calling an EGM.}

>>>>

% Custom section numbering and metadata
%'
%' This bit was really annoying, basically we treat sections as top-level
%' titles like in the Book document class. We don't want to number them.
%' Just hiding the section numbering with titlesec means that there's an
%' extra padded section number in front of a given subsection.
%' There are other simpler tricks to do this but these then have the
%' problem of no continuation across sections, i.e. the subsections start
%' numbered from 1 again in each new section!
%'
%' Partly via: https://tex.stackexchange.com/questions/80113/hide-section-numbers-but-keep-numbering/80114#80114
\makeatletter
\AtBeginDocument{
  \hypersetup{
    colorlinks = false,
    linkbordercolor = {cyan},
    pdftitle = {\@title},
    pdfauthor = {Glasgow Hackerspace CIC},
  }
}
\renewcommand\thesection{\@arabic\c@section}
\renewcommand\thesubsection{\@arabic\c@subsection}
\renewcommand\thesubsubsection{\@arabic\c@subsection.\@arabic\c@subsubsection}
\makeatother

@@

\begin{document}
\renewcommand\contentsname{
    \centering\bfseries\Large{Index to the Articles}\justifying
}

@@

\subsubsection[Directors' remote decision-making]{A decision which is made in accordance with \fancyref{subsubsubsection:unanimous} shall be as valid and effectual as if it had been passed at a meeting duly convened and held, provided the following conditions are complied with:}\label{subsubsubsection:remotedecision}
\begin{subindentpara}
  \item approval from each Director must be received by one person being either such person as all the Directors have nominated in advance for that purpose or such other person as volunteers if necessary (``the Recipient''), which person may, for the avoidance of doubt, be one of the Directors;
  \item following receipt of responses from all of the Directors, the Recipient must communicate to all of the Directors by any means whether the resolution has been formally approved by the Directors in accordance with this \fancyref{subsubsubsection:remotedecision};
  \item the date of the decision shall be the date of the communication from the Recipient confirming formal approval;
  \item the Recipient must prepare a minute of the decision in accordance with the \fancyref{subsection:minutes}.
\end{subindentpara}
\subsection{Conflicts of interest}
\subsubsection[Directors must declare Conflict of Interests]{Whenever a Director finds themselves in a situation that is reasonably likely to give rise to a Conflict of Interest, they must declare their interest to the Directors unless, or except to the extent that, the other Directors are or ought reasonably to be aware of it already.}
\subsubsection[Directors may debate a potential Conflict of Interest]{If any question arises as to whether a Director has a Conflict of Interest, the question shall be decided by a majority decision of the other Directors.}
\subsubsection[Directors' participation in meetings and Conflict of Interest]{Whenever a matter is to be discussed at a meeting or decided in accordance with \fancyref{subsubsection:withoutmeeting} and a Director has a Conflict of Interest in respect of that matter then, subject to \fancyref{subsubsection:authconflict}, they must:}\label{subsubsubsection:directornovote}
\begin{subindentpara}
  \item remain only for such part of the meeting as in the view of the other Directors is necessary to inform the debate;
  \item not be counted in the quorum for that part of the meeting; and
  \item withdraw during the vote and have no vote on the matter.
\end{subindentpara}
\subsubsection[Disclosure of confidential information relating to Director's Conflict of Interest]{When a Director has a Conflict of Interest which they have declared to the Directors, they shall not be in breach of their duties to the Company by withholding confidential information from the Company if to disclose it would result in a breach of any other duty or obligation of confidence owed by them.}
\subsubsection[Directors' voting at meetings and conflict of interest]{A Director must not vote at a board meeting (or at a meeting of a sub-committee) on any resolution which relates to a matter in which they have a personal interest or duty which conflicts (or may conflict) with the interests of the Hackerspace; they must withdraw from the meeting while an item of that nature is being dealt with.}\label{subsubsubsection:withdraw}
\subsubsection[Definition of a personal interest]{For the purposes of \fancyref{subsubsubsection:withdraw}: a Director will be deemed to have a personal interest in relation to a particular matter if a body in relation to which they are an Employee, Director, Officer or Elected Representative has an interest in the matter.}
\subsubsection[Quorum at Directors' meetings resulting from Conflict of Interest]{If, as a result of a Conflict of Interest (and the Directors have not authorised this Conflict of Interest) quorum at a Directors' meeting cannot be reached, the Directors must defer the decision to the membership by calling an EGM.}
